\section{Concluding Remarks}
\label{sec.concl}

This paper presented the $\pvslm$ tool for managing libraries for the
Prototype Verification System (PVS). This tool features support for
different library sources, libraries with several theories, and
dependencies among the theories (within the same library source).  The
tool is freely available for download and it is distributed under
GNU's GPLv3 license. It uses a small footprint language for
annotating libraries, which is described in full detail in BNF-like
notation in this paper. This paper also includes all commands
available from the tool, its architecture, and an overview of its
installation process.  A detailed step-by-step case study is included
for illustrating the main features of the tool.

As usual, much work remains to be done. First, it is important to make
available other PVS library sources with the help of the $\pvslm$
tool.  Also, it is important to test the tool against different
servers and in more operating systems. Finally, it would be highly
desirable for the tool to manage different versions of a library
source, each configured to work on different versions of PVS installed
in the host system. This will require an extension of the current
$\pvslm$ description language for annotating library sources.

\paragraph{\bf Acknowledgments.} The authors would like to thank
C. Mu\~noz in the NASA Langley Formal Methods Team for his
encouragement, ideas, and suggestions, specially for the help with the
definition of the metadata description language for packages.
