\section{Concluding Remarks}
\label{sec.concl}

This paper presented the $\pvslm$ tool for managing libaries for the
Prototype Verification System (PVS). This tool features support for
different library sources, libraries with several theories, and
dependencies among the theories (within the same library source).  The
tool is freely available for download and it is distributed under
GNU's GPLv3 license. The tool uses a small footprint language for
annotating libraries, which is described in full detail in BNF-like
notation in this paper. This paper also includes all commands
available from the tool, its architecture, and an overview of its
installation process.  A detailed step-by-step case study is included
for illustrating the main features of the tool.

As usual, much work remains to be done. First, it is important to make
available other library sources through the $\pvslm$ tool.  Also, it
is important to test the tool against different servers and in more
operating systems. Finally, it would be highly desirable for the tool
to manage different versions of a library source, which can depend on
the installed versions of PVS in the host system. This will likely
require an extension of the current metadata language for annotating
library sources.

\paragraph{\bf Acknowledgments.} The authors would like to thank
C. Mu\~noz from the NASA Langley Formal Methods Team for his
encouragement, ideas, and suggestions, specially for the help with the
definition of the metadata description language for packages.
